\documentclass[11pt]{article}
\usepackage{cite}
\usepackage{natbib}
\usepackage{amssymb}\usepackage{amsbsy}\usepackage{amsmath}

\begin{document}

\title{A List of Papers}
\author{put in this document by Jehane}
\date{November 7, 2014}
\maketitle

This is a LaTex document. Look! It really is! And this document has a bibliography, inserted using BibTex. This is the second bibliography I've made, and it was made using Zotero! wooohoo! I exported a group of sources from my Zotero into the BibTex format (.bib), and I didn't even have to export the whole library-- I could right-click on a selected group. These papers were written by Lizzie, like this oldie-but-goodie from 2009, "Invasive grass litter facilitates native shrubs through abiotic effects"~\citep{wolkovich_invasive_2009}.\\

\emph{This text should be beautiful and flowy and show up in italics.}\\

Look, here is another paragraph! It is so fun to write things that don't matter. blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah ~\citep{cook_divergent_2012}. blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah. ~\citep{pau_predicting_2011}\\

I think now it is time for a paragraph of text that also includes an equation. \(\epsilon*8*x^2\) To make this, I had to open math mode using a backslash and an open parentheses, and then close it with a backslash and a closed parentheses.\\

Some things on my desk currently:
\begin{enumerate}
\item a pencil\\
The pencil colors are:
\begin{itemize}
\item red
\item green
\item white
\end{itemize}
\item my lentil and yogurt lunch
\item a mug
\item my rite-in-the-rain
\end{enumerate}\\




\bibliographystyle{ea}
\bibliography{Wolkovich_papers}
\nocite{cook_divergent_2012, wolkovich_grass_2010, wolkovich_invasive_2009, cleland_phenological_2012, pau_predicting_2011, wilson_scavenging:_2011, wolkovich_phenology_2012, wolkovich_warming_2012}


\end{document}


